Dynamic Witnesses for Static Type Errors

### 2015-11-20 paper/pldi16-submission/introduction.tex
edit related

In this paper we propose a new approach to explaining type
\emph{static} type errors: by \emph{dynamically} witnessing
how exactly an ill-typed program goes wrong.
%
We have developed \toolname, an interactive tool that uses
the source of the ill-typed function to automatically synthesize
the result on the right in Figure~\ref{fig:factorial}, which
shows how the recursive calls reduce to a configuration where
the program ``goes wrong'' --- \ie\ the @int@ value @1@ is to be
multiplied with the @bool@ value @true@.
We achieve this via three concrete contributions.

>>>>

In this paper we propose a new approach that explains 
static type errors by \emph{dynamically} witnessing
how exactly an ill-typed program goes wrong.
%
We have developed \toolname, an interactive tool that uses
the source of the ill-typed function to automatically synthesize
the result on the right in Figure~\ref{fig:factorial}, which
shows how the recursive calls reduce to a configuration where
the program ``goes wrong'' --- \ie\ the @int@ value @1@ is to be
multiplied with the @bool@ value @true@.
We achieve this via three concrete contributions.
